---
title: "Iris Prediction App"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About The Iris Prediction App

This app uses the iris data set to predict sepal length based on the following inputs:

- Sepal width (number input)
- Petal length (number input)
- Petal width (number input)
- Species (radio button input)

In addition, there is a plot showing the values in the data set (coloured by species) and the predicted value. The Y-axis is *always* sepal length; the X-axis can be changed to sepal width, petal length, or petal width.

Once the **Go!** button is clicked, the predicted value is displayed, and the plot is updated.

## Prediction Model

The prediction model used in the app is quite simple:
```{r, comment = ''}
as.formula(lm(Sepal.Length ~ Sepal.Width +
                Petal.Length + Petal.Width + Species, data = iris))
```

The default values when the app is first opened are:

- sepal width = 3.5
- petal length = 1.4
- petal width = 0.2
- species = setosa

### You can find the app here (link)

## Default Prediction

The default predicted value for sepal length  when the app is opened is:

```{r, echo = T, comment = ''}
mod <- lm(Sepal.Length ~ Sepal.Width + 
            Petal.Length + Petal.Width + 
            Species, data = iris)

pred <- predict(mod, 
                newdata = data.frame(
                  Sepal.Width = 3.5,
                  Petal.Length = 1.4,
                  Petal.Width = 0.2,
                  Species = 'setosa'))

unname(round(pred, 1))
```

## Default Plot

Based on the default values listed above, as well as the default choice of sepal width being the x axis for the plot, the default plot for the app is shown below.

```{r, warning = F}
library(ggplot2)
iris_plot <- ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 2) +
  geom_point(aes(x = 3.5, y = pred, colour="black", size = 2), show.legend = F) +
  ylab('Sepal Length') + xlab('Sepal Width') + 
  scale_colour_manual(breaks=c("black", "setosa", "versicolor", "virginica"),
                      labels=c("Prediction", "Setosa", "Versicolor", "Virginica"),
                      values = c('black', '#F8766D', '#00BFC4', '#C77CFF')) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) 
           
iris_plot
```



